Rule-Based Preordering on Multiple Syntactic Levels \\in Statistical Machine Translation

### 2014-09-25 Paper/paper.tex
.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please make sure to keep technical paper submissions anonymous  !
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\name{Firstname Lastname}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \makeatletter
 \def\name#1{\gdef\@name{#1\\}}
 \makeatother
% \name{{\em Ge Wu, Yuqi Zhang, Alex Waibel}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

@@

We have also found improvements in the sentence structure. Table~\ref{t1} and Table~\ref{t2} shows some translation examples in both translation directions. Sections are separated by double lines in the table. Each section of this table shows one translation example with the source sentence (\emph{source}), translation without using MLT reordering (\emph{no MLT}), translation with MLT reordering (\emph{MLT}) and the reference (\emph{reference}). \emph{Glossary} for the source sentences or references in Chinese is also added as word for word translation. Each word or group of hyphenated words in the glossary corresponds a Chinese character or a group of Chinese characters that are not separated with space. A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles generally. The translation without using MLT reordering comes from the configuration with highest BLEU score that didn't use MLT reordering. And the translation with MLT reordering comes from the configuration with highest BLEU score that used MLT reordering. From the examples, we can clearly see the improvements in sentence structure.

@@

Besides the improvement in BLEU scores, our preordering approach also showed improvement in the sentence structure of the translation. Considering sentences that have complicated structure only make up a small portion of the data, even a small improvement in the result can mean a big improvement in translating these complicated sentences.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please make sure to keep technical paper submissions anonymous  !
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\name{Firstname Lastname}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \makeatletter
 \def\name#1{\gdef\@name{#1\\}}
 \makeatother
% \name{{\em Ge Wu, Yuqi Zhang, Alexander Waibel}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

@@

We have also found improvements in the sentence structure. Table~\ref{t1} and Table~\ref{t2} show some translation examples in both translation directions. Sections are separated by double lines in the table. Each section of this table shows one translation example with the source sentence (\emph{source}), translation without using MLT reordering (\emph{no MLT}), translation with MLT reordering (\emph{MLT}) and the reference (\emph{reference}). \emph{Glossary} for the source sentences or references in Chinese is also added as word for word translation. Each word or group of hyphenated words in the glossary corresponds a Chinese character or a group of Chinese characters that are not separated with space. A placeholder $\Box$ is used to replace words that are difficult to translate, which play grammatical roles generally. The translation without using MLT reordering comes from the configuration with highest BLEU score that didn't use MLT reordering. And the translation with MLT reordering comes from the configuration with highest BLEU score that used MLT reordering. From the examples, we can clearly see the improvements in sentence structure.

@@

Besides the improvement in BLEU scores, our preordering approach also showed improvement in the sentence structure of the translation. Considering sentences that have complicated structure only make up a small part of the data, even a small improvement in the result can mean a big improvement in translating these complicated sentences.
